The Causal Effect of Media Frames on Issue Attitudes

### 2021-09-29 paper/main.tex

This is however not the case.

% show for one specific case that shift in media frame corresponded to 
\begin{table}[!htbp] \centering 
  \caption{Individual-level Model} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & Immigration attitude & Integration attitude \\ 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 Lagged DV & 0.793$^{***}$ & 0.664$^{***}$ \\ 
  &  & (0.004) \\ 
  & & \\ 
 Petty Crime & 0.0001 & 0.002 \\ 
  & (0.002) & (0.004) \\ 
  & & \\ 
 Capital Crime & 0.033$^{***}$ & $-$0.027$^{**}$ \\ 
  & (0.006) & (0.012) \\ 
  & & \\ 
 Refugee Numbers & $-$0.016$^{***}$ & $-$0.001 \\ 
  & (0.002) & (0.004) \\ 
  & & \\ 
 Refugee Camps & 0.025$^{***}$ & $-$0.004 \\ 
  & (0.004) & (0.012) \\ 
  & & \\ 
 Mediterranean S\&R & 0.035$^{***}$ & $-$0.005 \\ 
  & (0.002) & (0.005) \\ 
  & & \\ 
 Labour Market & 0.015$^{***}$ & 0.009 \\ 
  & (0.003) & (0.006) \\ 
  & & \\ 
 Deportation & $-$0.002$^{***}$ & 0.002$^{**}$ \\ 
  & (0.001) & (0.001) \\ 
  & & \\ 
 Constant & 0.045$^{***}$ & $-$0.288$^{***}$ \\ 
  & (0.015) & (0.036) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 88,026 & 36,180 \\ 
R$^{2}$ & 0.617 & 0.421 \\ 
Adjusted R$^{2}$ & 0.617 & 0.421 \\ 
Residual Std. Error & 1.095 (df = 88017) & 1.095 (df = 36171) \\ 
F Statistic & 17,740.240$^{***}$ (df = 8; 88017) & 3,286.942$^{***}$ (df = 8; 36171) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

This is however not the case. As figure \ref{fig:did_corr} shows, even with different specifications, \textit{no} estimate has predictive power for our analysis. For example, in the upper left panel 'crime', we can see 5 different lags 'g', '6m', '1m', '1w', '1d' distinguished vertically, and the effects for two different issues in the two different panes. Additionally, the color of the points indicates whether the model was estimated only for readers of a single newspaper (lower N, but no treatment diffusion) or all readers of a newspaper (who might read another newspaper, say SZ readers who also read FAZ). All estimates are clearly clustering around the null, indicating no effect. While the 'exclusive reader' estimates show more variation, they also indicate far broader confidence intervals. There is no considerable difference across lags, and the variables only differ by the broader confidence intervals of the integration variable, owing to the fewer waves including this question. Generally, this analysis indicates no effect of media framing of migration on migration attitudes.

To corroborate these results, I estimate another model directly predicting individual migration opinions with a lagged dependent and individual estimates of consumed migration frames (see section \ref{sec:models}). The results for migration and integration attitudes can be seen in table \ref{tab:ind_model}. While the
